|

### 2023-05-09 paper/01-introduction.Rmd
figures + tables formatting

Pro football focus (PFF) defines pass-rush productivity as: 
$$
\frac{\frac{1}{2}(\# Hurries + \# Hits) + \# Sacks}{\#PassRush Snaps}
$$.

This metric gives twice as much weight to a sack relative to hurries and hits, which is a slight improvement, but the choice of weights is ad-hoc an still only measures binary outcomes similar to the shortcomings of previously discussed metrics.   (https://www.pro-football-reference.com/about/advanced_stats.htm)

@@

\begin{table}
\caption{A summary of previously-existing pass rush metrics. \label{tab:metrics}}
\begin{center}
\begin{tabular}{ll}
\textbf{Metric} & \textbf{Description}\\\hline
Sacks & A defensive player tackles the quarterback behind the line of scrimmage before the quarterback is able to throw a pass \\
Hits & A defensive player tackles the quarterback behind the line of scrimmage after the quarterback is able to throw a pass. \\
Hurries & A defensive player pressures the quarterback behind the line of scrimmage such that the quarterback must release the ball prior sooner than they wanted to. \\
QB Pressures & A sack, hit, or hurry. \\
Pass-Rush Productivity (PRP) & $\frac{\frac{(\# Hurries + \# Hits)}{2} + \# Sacks}{\#PassRush Snaps}$\\
Time In Pocket (TIP) & The time from snap to throw or pocket collapse for a quarterback \\
Pass Rush Win Rate (PRWR) & Rate at which pass rusher beats pass block within 2.5 seconds after snap\\\hline
\end{tabular}
\end{center}
\end{table}

>>>>

Pro football focus (PFF) defines pass-rush productivity as 
$$[ \ (\text{Hurries} + \text{Hits})/2 + \text{Sacks} \ ]\  / \text{ Pass Rush Snaps}$$
This metric gives twice as much weight to a sack relative to hurries and hits, which is a slight improvement, but the choice of weights is ad-hoc an still only measures binary outcomes similar to the shortcomings of previously discussed metrics.   (https://www.pro-football-reference.com/about/advanced_stats.htm)

@@

\begin{table}
\caption{A summary of previously-existing pass rush metrics. \label{tab:metrics}}
\centering
\begin{tabular}{p{0.27\textwidth}p{0.67\textwidth}}
  \hline
Metric & Description \\ 
  \hline
Sacks & A defender tackles the QB behind the line of scrimmage before the QB is able to throw a pass \\
Hits & A defender tackles the QB behind the line of scrimmage after the QB is able to throw a pass. \\
Hurries & A defender pressures the QB behind the line of scrimmage such that the QB must release the ball prior sooner than they wanted to. \\
Pressures & $\text{Hurries} + \text{ Hits } + \text{ Sacks}$ \\
Pass-Rush Productivity & $[\ (\text{Hurries} + \text{Hits})/2 + \text{Sacks}\ ]\  / \text{ Pass Rush Snaps}$\\
Time In Pocket & Time (in seconds) between ball snap and throw or pocket collapse for a QB \\
Pass Rush Win Rate & Rate at which pass rusher beats pass block within 2.5 seconds after ball snap\\
   \hline
\end{tabular}
\end{table}

[Pro football ref has different QB pressures formula? https://www.pro-football-reference.com/about/advanced_stats.htm]

### 2023-05-09 paper/04-results.Rmd
figures + tables formatting

```{r}
#| label: fig_predictability
#| fig.cap: "strain is more predictive of pressure rate than pressure rate itself."
#| fig.width: 4
#| fig.height: 3
#| fig.show: "hold"
source(here("scripts", "07_fig_predictability.R"))
hsh_hsh
strain_hsh
```

>>>>

```{r}
#| label: fig_predictability
#| fig.cap: "strain is more predictive of pressure rate than pressure rate itself."
#| fig.width: 6.5
#| fig.height: 3
#| fig.show: "hold"
source(here("scripts", "07_fig_predictability.R"))
fig_predictability
```
